[dcpo_demsupport]

### 2020-05-31 paper/dcpo_demsupport.Rmd
adding replication codes for model 5; improve the replicability of the rmd

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "[dcpo_demsupport]"
thanks: "Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Yuehong 'Cassandra' Tai
  affiliation: University of Iowa
- name: Yue Hu
  affiliation: Tsinghua University
- name: Frederick Solt
  affiliation: University of Iowa
abstract: ""
keywords: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$"))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
nocite: |
  @Solt2020a
---

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# load all the packages you will use below 
library(huxtable)
library(kableExtra)
library(DCPOtools)
library(tidyverse)
library(latex2exp)
```

@@

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: https://raw.githubusercontent.com/junkpolisci/website/master/working_content/svm-latex-ms2.tex
title: "[dcpo_demsupport]"
thanks: "Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Yuehong 'Cassandra' Tai
  affiliation: University of Iowa
- name: Yue Hu
  affiliation: Tsinghua University
- name: Frederick Solt
  affiliation: University of Iowa
abstract: ""
keywords: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
# biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
nocite: |
  @Solt2020a
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 300)

# If you haven't install `DCPOtools`
# remotes::install_github("fsolt/DCPOtools")

if (!require(pacman)) install.packages("pacman")
library(pacman)

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  huxtable, kableExtra, # tabulation
  latex2exp, # visualization
  purrr, broom, tidyverse
) # data wrangling # data wrangling

# Functions preload
set.seed(313)
```

@@

```{r replication-model5, eval = FALSE}
# Before running the following lines, one should set their personal token and server in their system environment first: 
# Sys.setenv("DATAVERSE_KEY" = "exampleToken")
# Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")

supdem <- get_file("Support for democracy.tab", "doi:10.7910/DVN/A47LUM") %>% 
  read_csv

# Required by the replication file
p_load(
  countrycode,
  MASS,
  psych,
  arm,
  loo,
  rstanarm,
  RColorBrewer,
  devtools,
  dgo
)

sddem1 = gather(data=supdem, key="Item", value="Response", 6:33, na.rm=TRUE) 
sddem1$Sample = 0
sddem1[sddem1$Project=="AfB", "Sample"] = sddem1[sddem1$Project=="AfB", "AfB_sample"]
sddem1[sddem1$Project=="ArB", "Sample"] = sddem1[sddem1$Project=="ArB", "ArB_sample"]
sddem1[sddem1$Project=="AsB", "Sample"] = sddem1[sddem1$Project=="AsB", "AsB_sample"]
sddem1[sddem1$Project=="AsnB", "Sample"] = sddem1[sddem1$Project=="AsnB", "AsnB_sample"]
sddem1[sddem1$Project=="ESS", "Sample"] = sddem1[sddem1$Project=="ESS", "ESS_sample"]
sddem1[sddem1$Project=="LAPOP", "Sample"] = sddem1[sddem1$Project=="LAPOP", "LAPOP_sample"]
sddem1[sddem1$Project=="LB", "Sample"] = sddem1[sddem1$Project=="LB", "LB_sample"]
sddem1[sddem1$Project=="NDB", "Sample"] = sddem1[sddem1$Project=="NDB", "NDB_sample"]
sddem1[sddem1$Project=="Pew", "Sample"] = sddem1[sddem1$Project=="Pew", "Pew_sample"]
sddem1[sddem1$Project=="WVS", "Sample"] = sddem1[sddem1$Project=="WVS", "WVS_sample"]
sddem1[sddem1$Project=="CSES", "Sample"] = sddem1[sddem1$Project=="CSES", "CSES_sample"]

# trim stacked dataset
sddem1 = sddem1[, -c(6:16)]
sddem1$Response = ifelse(sddem1$Response==0, NA, sddem1$Response)
sddem1 = sddem1[!is.na(sddem1$Response), ]

# create item by project indicators
sddem1 = unite(sddem1, ItemProj, c(Project, Item), sep = "_", remove = FALSE)
sddem1$ItemProj = as.factor(sddem1$ItemProj)

# create year by country indicators
year0 = 1990
sddem1 = sddem1[sddem1$Year > year0,]
sddem1 = unite(sddem1, YearCountry, c(Year, Country), sep = "_", remove = FALSE)
sddem1$YearCountry = as.factor(sddem1$YearCountry)

# create item by project by country indicators
sddem1 = unite(sddem1, ItemProjCnt, c(ItemProj, Country), sep = "_", remove = FALSE)
sddem1$ItemProjCnt = as.factor(sddem1$ItemProjCnt)

# create item by country indicators
sddem1 = unite(sddem1, ItemCnt, c(Item, Country), sep = "_", remove = FALSE)
sddem1$ItemCnt = as.factor(sddem1$ItemCnt)

# create year by project indicators
sddem1 = unite(sddem1, YrProj, c(Year, Project), sep = "_", remove = FALSE)
sddem1$YrProj = as.factor(sddem1$YrProj)

# create year by project by country indicators
sddem1 = unite(sddem1, YrProjCnt, c(YrProj, Country), sep = "_", remove = FALSE)
sddem1$YrProjCnt = as.factor(sddem1$YrProjCnt)

# factorise
sddem1$Country = as.factor(as.character(sddem1$Country))
sddem1$Item = as.factor(as.character(sddem1$Item))
sddem1$ItemProj = as.factor(as.character(sddem1$ItemProj))
sddem1$ItemCnt = as.factor(as.character(sddem1$ItemCnt))
sddem1$ItemProjCnt = as.factor(as.character(sddem1$ItemProjCnt))
sddem1$Project = as.factor(as.character(sddem1$Project))
sddem1$YrProj = as.factor(as.character(sddem1$YrProj))
sddem1$YrProjCnt = as.factor(as.character(sddem1$YrProjCnt))
sddem1$Year = as.factor(sddem1$Year-year0)

# drop countries with less than 2 years of data
cnt.obs.years = rowSums(table(sddem1$Country, sddem1$Year) > 0)
sddem2 = sddem1[sddem1$Country %in% levels(sddem1$Country)[cnt.obs.years > 1], ]

## Stan estimation

# prepare data for stan

n.items = length(unique(sddem2$Item))
n.cntrys = length(unique(sddem2$Country))
n.yrs = 2015-year0
n.proj = length(unique(sddem2$Project))
n.resp = dim(sddem2)[1]
n.itm.prj = length(unique(sddem2$ItemProj))
n.itm.cnt = length(unique(sddem2$ItemCnt))
n.cntry.yrs = n.cntrys * n.yrs
n.itm.prj.cnt = length(unique(sddem2$ItemProjCnt))
n.yr.proj.cnt = length(unique(sddem2$YrProjCnt))
cntrys = as.numeric(factor(sddem2$Country))
cnt.names = sort(unique(sddem2$Country))
cnt.ccode = sddem2[match(cnt.names, sddem2$Country), "COWCode"]
items = as.numeric(factor(sddem2$Item))
yrs = as.numeric(sddem2$Year)
projs = as.numeric(factor(sddem2$Project))
itm.prjs = as.numeric(factor(sddem2$ItemProj))
itm.prj.cnts = as.numeric(factor(sddem2$ItemProjCnt))
itm.cnts = as.numeric(factor(sddem2$ItemCnt))
cntry.yrs = as.numeric(sddem2$YearCountry)

# specify data for stan
dat.2 = list(N=n.resp, K=n.itm.prj, T=n.yrs, J=n.cntrys, P=n.itm.prj.cnt, jj=cntrys, tt=yrs, 
             pp=itm.prj.cnts, kk=itm.prjs, x=sddem2$Response, samp=sddem2$Sample)

# pars
pars.5 = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta","x_pred","log_lik")

# set pars for final run (time-consuming; reduce iterations for trial run)
n.iter = 1000
n.warm = 500
n.chn = 4
n.thin = 2

## supdem.stan.mod5.stan obtained from dataverse replication files
stan.mod.5 <- stan(file = "supdem.stan.mod5.stan", data=dat.2, pars=pars.5, 
                   iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
                   control=list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
```
